Technical Report

### 2018-06-29 fully-abstract-comp/ftlr-proof-cases.tex

\begin{lemma}
  \label{lem:sealed-lrv-lrexj}
  If
  \begin{itemize}
  \item $\npair{(\sealed{\sigma,\vsc_1},\sealed{\sigma,\vsc_1'})} \in \lrvg{\trust}(W_{R,1})$
  \item $\npair{(\sealed{\sigma,\vsc_2},\sealed{\sigma,\vsc_2'})} \in \lrvg{\trust}(W_{R,2})$ 
  \item $\nonExec{\vsc_1'}$ and $\nonExec{\vsc_2'}$
  \item $W_{R,1} \oplus W_{R,2}$ is defined
  \end{itemize}
  Then
  \begin{itemize}
  \item $\npair{(\vsc_1,\vsc_2,\vsc_1',\vsc_2')} \in \lrexj(W_{R,1}\oplus W_{R,2})$
  \end{itemize}
\end{lemma}
\begin{proof}
  TODO
\end{proof}

@@

  In the second case (xjmp), we have that $\npair{(\Phi_S(r_1),\Phi_T(r_1))} \in \lrvg{\trust}(W_{R,1})$, $\npair{(\Phi_S(r_2),\Phi_T(r_2))} \in \lrvg{\trust}(W_{R,2})$ and $\npair{(\Phi_S'',\Phi_T'')} \in \lrrg{\trust}(W_R')$ for some $W_{R,1}, W_{R,2}, W_R'$ with $W_R = W_{R,1} \oplus W_{R,2} \oplus W_R'$.

  Using the facts that $\Phi_S(r_1) = \sealed{\sigma,c_1}$ and $\Phi_S(r_2) = \sealed{\sigma,c_2}$ and $\Phi_T(r_1) = \sealed{\sigma,c_1'}$ and $\Phi_T(r_2) = \sealed{\sigma,c_2'}$ and $\nonExec{\Phi_S(r_2)}$ and $\nonExec{\Phi_T(r_2)}$, and the above points, Lemma~\ref{lem:sealed-lrv-lrexj} tells us that $\npair{(c_1,c_2,c_1',c_2')} \in \lrexj(W_{R,1} \oplus W_{R,2})$.

  TODO
\end{proof}

@@

\begin{lemma}
  \label{lem:stack-sat-unchanged-future}
  If $\pwfree = \pwfree[W']$ and $W' \future W$ and
  $\memSatFStack{\ms_\stk,\ms_T}{W}$, then $\memSatFStack{\ms_\stk,\ms_T}{W'}$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

\begin{lemma}
  \label{lem:heap-sat-unchanged-future}
  If $\pwheap[\purePart{W}] = \pwheap[\purePart{W'}]$ and $W_{h}' \future W_h$ and $\npair{(\overline{\sigma},\ms_S,\ms_T)} \in \lrheap(\pwheap[W])(W_h)$, then $\npair{(\overline{\sigma},\ms_S,\ms_T)} \in\lrheap(\pwheap[W'])(W_h')$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

>>>>

\begin{lemma}
  \label{lem:sealed-lrv-lrexj}
  If
  \begin{itemize}
  \item $\npair{(\sealed{\sigma,\vsc_1},\sealed{\sigma,\vsc_1'})} \in \lrvg{\trust}(W_{R,1})$
  \item $\npair{(\sealed{\sigma,\vsc_2},\sealed{\sigma,\vsc_2'})} \in \lrvg{\trust}(W_{R,2})$ 
  \item $\nonExec{\vsc_1'}$ and $\nonExec{\vsc_2'}$
  \item $W_{R,1} \oplus W_{R,2} \oplus W_M$ is defined
  \item $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$
  \end{itemize}
  Then
  \begin{itemize}
  \item $\npair[n-1]{(\vsc_1,\vsc_2,\vsc_1',\vsc_2')} \in \lrexj(W_{R,1}\oplus W_{R,2})$
  \end{itemize}
\end{lemma}
\begin{proof}
  From $\npair{(\sealed{\sigma,\vsc_1},\sealed{\sigma,\vsc_1'})} \in \lrvg{\trust}(W_{R,1})$, we know that
  \begin{itemize}
  \item $(\isLinear{\src{\vsc_1}} \text{ iff } \isLinear{\vsc_1'})$ 
  \item $\exists r \in \dom(\pwheap), \sigrets,\sigcloss,\mscode \ldotp$ 
  \item $\pwheap[W_{R,1}](r) = (\pure,\_,H_\sigma)$ 
  \item $H_\sigma \nequal H^\mathrm{code,\square}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc$
  \item $\npair[n']{\stpair[.]{\vsc_1}{\vsc_1'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,1})$ for all $n' < n$
  \item If $(\isLinear{\src{\vsc_1}}$ then for all $W' \future W_{R,1}$, $W_o$, $n' < n$, $\npair[n']{\stpair[.]{\vsc_2}{\vsc_2'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_o)$, we have that
    \begin{equation*}
      \npair[n']{\src{\vsc_1},\src{\vsc_2},\vsc_1',\vsc_2'} \in \lrexj(W'\oplus W_o))
    \end{equation*}
  \item If $(\nonLinear{\src{\vsc_1}}$ then for all $W' \future \purePart{W_{R,1}}$, $W_o$, $n' < n$, $\npair[n']{\stpair[.]{\vsc_2}{\vsc_2'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_o)$, we have that
    \begin{equation*}
      \npair[n']{\src{\vsc_1},\src{\vsc_2},\vsc_1',\vsc_2'} \in \lrexj(W'\oplus W_o))
    \end{equation*}
  \end{itemize}

  From $\npair{(\sealed{\sigma,\vsc_2},\sealed{\sigma,\vsc_2'})} \in \lrvg{\trust}(W_{R,2})$, we know that
  \begin{itemize}
  \item $(\isLinear{\src{\vsc_2}} \text{ iff } \isLinear{\vsc_2'})$ 
  \item $\exists r' \in \dom(\pwheap), \sigrets,\sigcloss,\mscode \ldotp$ 
  \item $\pwheap[W_{R,2}](r') = (\pure,\_,H_\sigma)$ 
  \item $H_\sigma \nequal H^\mathrm{code,\square}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc$
  \item $\npair[n']{\stpair[.]{\vsc_2}{\vsc_2'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$ for all $n' < n$
  \end{itemize}

  From $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$, we know that two different regions cannot have $H_\sigma$ defined for the same $\sigma$, so that $r = r'$.
  Both when $\isLinear{\vsc_1}$ and when $\nonLinear{\vsc_1}$ (using Lemma~\ref{lem:world-fut-purePart}), we know that for all $W' \future W_{R,1}$, $W_o$, $n' < n$, $\vsc_2$, $\vsc_2'$, $\npair[n']{\stpair[.]{\vsc_2}{\vsc_2'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_o)$, we have that
  \begin{equation*}
    \npair[n']{\src{\vsc_1},\src{\vsc_2},\vsc_1',\vsc_2'} \in \lrexj(W'\oplus W_o))
  \end{equation*}
  We can now instantiate this fact with $W' = W_{R,1}$, $W_o = W_{R,2}$, $n' = n-1$, and the fact that $\npair[n-1]{\stpair[.]{\vsc_2}{\vsc_2'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$ (see above) to conclude
  \begin{equation*}
    \npair[n-1]{\src{\vsc_1},\src{\vsc_2},\vsc_1',\vsc_2'} \in \lrexj(W_{R,1}\oplus W_{R,2})\text{.}
  \end{equation*}
\end{proof}

@@

  In the second case (xjmp), we have that $\npair{(\Phi_S(r_1),\Phi_T(r_1))} \in \lrvg{\trust}(W_{R,1})$, $\npair{(\Phi_S(r_2),\Phi_T(r_2))} \in \lrvg{\trust}(W_{R,2})$ and $\npair{(\Phi_S'',\Phi_T'')} \in \lrrg{\trust}(\{r_1,r_2\})(W_R')$ for some $W_{R,1}, W_{R,2}, W_R'$ with $W_R = W_{R,1} \oplus W_{R,2} \oplus W_R'$.

  Using the facts that $\Phi_S(r_1) = \sealed{\sigma,c_1}$ and $\Phi_S(r_2) = \sealed{\sigma,c_2}$ and $\Phi_T(r_1) = \sealed{\sigma,c_1'}$ and $\Phi_T(r_2) = \sealed{\sigma,c_2'}$ and $\nonExec{\Phi_S(r_2)}$ and $\nonExec{\Phi_T(r_2)}$, and the above points, Lemma~\ref{lem:sealed-lrv-lrexj} tells us that $\npair[n-1]{(c_1,c_2,c_1',c_2')} \in \lrexj(W_{R,1} \oplus W_{R,2})$.

  By definition of $\lrexj$, it suffices to prove that
  \begin{itemize}
  \item
    \begin{equation*}
      \npair[n-1]{\left(\array{l}\Phi_S.\reg\update{r_1,r_2}{\linCons{c_1},\linCons{c_2}},\\ \Phi_T.\reg\update{r_1,r_2}{\linCons{c_1'},\linCons{c_2'}}\endarray\right)} \in
      \lrr(\{\rdata\})(W_R')
    \end{equation*}

    It is easy to show that $\npair{\linCons{c_1},\linCons{c_1'}} \in \lrvg{\trust}(\purePart{W_{R,1}})$ and $\npair{\linCons{c_2},\linCons{c_2'}} \in \lrvg{\trust}(\purePart{W_{R,2}})$, by using Lemma~\ref{lem:non-linear-pure} in the non-linear case and the fact that $0$ is always related to itself by definition of $\lrvg{\trust}$ in the linear case.
    We also have that $\purePart{W_R'} = \purePart{W_{R,1}} = \purePart{W_{R,2}}$ by Lemma~\ref{lem:purePart-oplus} and the fact that $W_R = W_{R,1} \oplus W_{R,2} \oplus W_R'$, so it follows that $\npair{\linCons{c_1},\linCons{c_1'}} \in \lrvg{\trust}(\purePart{W_R'})$ and $\npair{\linCons{c_2},\linCons{c_2'}} \in \lrvg{\trust}(\purePart{W_R'})$.
    From this and the fact that $\npair{(\Phi_S'',\Phi_T'')} \in \lrrg{\trust}(\{r_1,r_2\})(W_R')$, it follows easily that
    \begin{equation*}
      \npair[n-1]{\left(\array{l}\Phi_S.\reg\update{r_1,r_2}{\linCons{c_1},\linCons{c_2}},\\ \Phi_T.\reg\update{r_1,r_2}{\linCons{c_1'},\linCons{c_2'}}\endarray\right)} \in
      \lrrg{\trust}(\{\rdata\})(W_R')
    \end{equation*}

    From the fact that $\Phi_S$ is reasonable up to $n$ steps, tells us that $\Phi.\reg(r)$ is reasonable in memory $\Phi.\mem$ and free stack $\Phi.\ms_\stk$ up to $n-1$ steps for all $r \neq \pcreg$.
    Lemma~\ref{lem:trusted-and-reasonable-is-untrusted} then tells us that
    \begin{equation*}
      \npair[n-1]{\left(\array{l}\Phi_S.\reg\update{r_1,r_2}{\linCons{c_1},\linCons{c_2}},\\ \Phi_T.\reg\update{r_1,r_2}{\linCons{c_1'},\linCons{c_2'}}\endarray\right)} \in
      \lrr(\{\rdata\})(W_R')
    \end{equation*}
    using the fact that $n-1 > 0$ (by assumption above), Theorem~\ref{thm:ftlr} holds up to $n-1$ steps (by assumption).

  \item $\memSat[n-1]{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$
    Follows by Lemma~\ref{lem:downwards-closed} from the corresponding assumption of this lemma.

  \item $W_M \oplus W_R' \oplus W_{R,1} \oplus W_{R,2}$ is defined.

    This follows easily from the facts that $W_R = W_{R,1} \oplus W_{R,2} \oplus W_R'$ (see above) and the assumption that $W_\pcreg \oplus W_R' \oplus W_M'$ is defined.
  \end{itemize}
\end{proof}

@@

\begin{lemma}
  \label{lem:stack-sat-unchanged-future}
  If $\pwfree = \pwfree[W']$ and $W' \future W$ and
  $\memSatFStack{\ms_\stk,\ms_T}{W}$, then $\memSatFStack{\ms_\stk,\ms_T}{W'}$.
\end{lemma}
\begin{proof}
  Follows by inspecting the definition of $\memSatFStack{\ms_\stk,\ms_T}{W}$ and by the monotonicity of memory relations in the world.
\end{proof}

\begin{lemma}
  \label{lem:heap-sat-unchanged-future}
  If $\pwheap[\purePart{W}] = \pwheap[\purePart{W'}]$ and $W_{h}' \future W_h$ and $\npair{(\overline{\sigma},\ms_S,\ms_T)} \in \lrheap(\pwheap[W])(W_h)$, then $\npair{(\overline{\sigma},\ms_S,\ms_T)} \in\lrheap(\pwheap[W'])(W_h')$.
\end{lemma}
\begin{proof}
  Follows by inspecting the definition of $\lrheap$ and $\purePart{}$ and using the monotonicity of memory relations in the world.
\end{proof}

### 2018-06-29 fully-abstract-comp/technical-report.tex
Prove the jmp/jnz case of the FTLR.

      % This case was never used (?) so it is not necessary.
      % \wedge \\
      % \quad \npair[n']{\src{\vsc_S'},\src{\vsc_S},\vsc_T',\vsc_T} \in \lrexj(W' \oplus W_o)
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma_\baddr,\sigma_\eaddr,\sigma}},\\ \seal{\sigma_\baddr,\sigma_\eaddr,\sigma} \endarray \right)} 
    \; \middle| \;
    \begin{array}{l}
      [\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\gsigrets \cup \gsigcloss) \tand\\
      \forall \sigma' \in [\sigma_\baddr,\sigma_\eaddr] \ldotp \exists r \in \dom(\pwheap) \ldotp \\
      \quad \pwheap(r) = (\pure,\_,H_\sigma) \tand H_\sigma \; \sigma' \nequal (\lrv \circ \xi)
    \end{array}
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{l}
      \begin{array}{r l l}
        % \perm = \noperm & \Rightarrow & \npair{(\linear,\baddr,\eaddr)} \in \lrp(W) \wedge \\
        \perm \in \readAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \stackReadCond{W} \wedge \\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \stackWriteCond{W}
      \end{array}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      [b,e] \mathrel{\#} \ta \tand\\
      \begin{array}{r l l }
        % \perm = \noperm & \Rightarrow & \npair{(\lin,\baddr,\eaddr)} \in \lrp(W) \wedge \\
        \perm \in \readAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \readCond{\lin,W} \wedge\\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \writeCond{\lin,W} \wedge\\
        % we are excluding rwx pointers.
        \perm \neq \rwx \wedge \\
        % \perm = \rwx &\Rightarrow& \array[t]{l}\npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge \\
        %                            \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W} \endarray\\
        \perm = \rx &\Rightarrow& \array[t]{l}\npair{[\baddr,\eaddr]} \in \execCond{W} \wedge\\
        \npair{[\baddr,\eaddr]} \in \xReadCond{W} \wedge \\
                                  \lin = \normal \\ \endarray
      \end{array}
    \end{array}
    \right\}
  \end{array}
\]

@@

\begin{definition}[Reasonable configuration]
  \label{def:reasonable-conf}
  We say that an execution configuration $\Phi$ is reasonable up to $n$ steps with $(\ta,\stkb,\gsigrets,\gsigcloss)$ 
  iff for $n' \leq n$:
  \begin{itemize}
  \item \emph{Guarantee stack base address before call} If
    \begin{itemize}
    \item $\Phi$ points to $\src{\scall{\offpc,\offsigma}{r_1}{r_2}}$ in $\ta$
      for some $\src{r_1}$ and $\src{r_2}$
    \end{itemize}
    Then all of the following hold:
    \begin{itemize}
    \item $\src{\Phi}(\src{r_\stk}) =
      \src{\stkptr{\_,\stkb,\_,\_}}$
    \item $r_1 \neq \rtmp{1}$
    \item $\Phi(\pcreg) + \calllen$ behaves reasonably up to $n'-1$ steps
    \end{itemize}
  \item \emph{Use return seals only for calls, use closure seals appropriately} If
    \begin{itemize}
    \item $\src{\Phi}$ points to $\src{\tcseal{r_1}{r_2}}$ in $\ta$ and $\Phi(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$
    \end{itemize}
    Then one of the following holds:
    \begin{itemize}
    \item $\src{\Phi}$ is inside $\src{\scall{\offpc,\offsigma}{r_1'}{r_2'}}$ and $\sigma \in \gsigrets$
    \item $\sigma \in \gsigcloss$ and one of the following holds:
      \begin{itemize}
      \item $\exec{\Phi(r_2)}$ and $\Phi(r_2)$ behaves reasonably up to $n' - 1$ steps.
      \item $\nonExec{\Phi(r_2)}$ and $\Phi(r_2)$ is reasonable up to $n' - 1$ steps in memory $\Phi.\ms$ and free stack $\Phi.\ms_\stk$.
      \end{itemize}
    \end{itemize}
  \item \emph{Don't store private stuff...} If
    \begin{itemize}
    \item $\src{\Phi}$ points to $\src{\tstore{r_1}{r_2}}$ in $\ta$, then
    \end{itemize}
    Then $\Phi.\reg(r_2)$ is reasonable in memory $\Phi.\mem$ up to $n' -1$ step
  \item \emph{Don't leak private stuff...} If
    \begin{itemize}
    \item $\Phi \step[\ta,\stkb] \Phi'$
    \end{itemize}
    Then one of the following holds:
    \begin{itemize}
    \item All of the following hold:
      \begin{itemize}
      \item $\Phi'.\reg(\pcreg) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr')$ and $\Phi.\reg(\pcreg) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr)$
      \item $\Phi'$ is reasonable up to $n'-1$ steps
      \end{itemize}
      % \dominique{the following seems unnecessary: why would we allow trusted code to use a jump instruction to jump out of a trusted component? it can use call and xjmp for calls/returns/tailcalls}
    % \item $\Phi'.\reg(r)$ is reasonable in memory $\Phi'.\mem$ and free stack $\Phi'.\ms_\stk$ up to $n'-1$ steps for all $r$ (including $\pcreg$)
    \item
      \begin{itemize}
      \item $\Phi$ points to $\src{\scall{\offpc,\offsigma}{r_1}{r_2}}$ for some $\src{r_1}$ and $\src{r_2}$
      \item $\Phi.\reg(r)$ is reasonable in memory $\Phi.\mem$ and free stack $\Phi.\ms_\stk$ up to $n'-1$ steps for all $r \neq \pcreg$
      \end{itemize}
    \item
      \begin{itemize}
      \item $\Phi$ points to $\src{\txjmp{\offpc,\offsigma}{r_1}{r_2}}$ for some $\src{r_1}$ and $\src{r_2}$
      \item $\Phi.\reg(r)$ is reasonable in memory $\Phi.\mem$ and free stack $\Phi.\ms_\stk$ up to $n'-1$ steps for all $r \neq \pcreg$
      \end{itemize}
    \end{itemize}
  \end{itemize}
\end{definition}

>>>>

      % This case was never used (?) so it is not necessary.
      % \wedge \\
      % \quad \npair[n']{\src{\vsc_S'},\src{\vsc_S},\vsc_T',\vsc_T} \in \lrexj(W' \oplus W_o)
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma_\baddr,\sigma_\eaddr,\sigma}},\\ \seal{\sigma_\baddr,\sigma_\eaddr,\sigma} \endarray \right)} 
    \; \middle| \;
    \begin{array}{l}
      [\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\gsigrets \cup \gsigcloss) \tand\\
      \forall \sigma' \in [\sigma_\baddr,\sigma_\eaddr] \ldotp \exists r \in \dom(\pwheap) \ldotp \\
      \quad \pwheap(r) = (\pure,\_,H_\sigma) \tand H_\sigma \; \sigma' \nequal (\lrv \circ \xi)
    \end{array}
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{l}
      \begin{array}{r l l}
        \perm \not\in \{\rx,\rwx\} \wedge\\
        % \perm = \noperm & \Rightarrow & \npair{(\linear,\baddr,\eaddr)} \in \lrp(W) \wedge \\
        \perm \in \readAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \stackReadCond{W} \wedge \\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \stackWriteCond{W}
      \end{array}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      [b,e] \mathrel{\#} \ta \tand\\
      \begin{array}{r l l }
        % \perm = \noperm & \Rightarrow & \npair{(\lin,\baddr,\eaddr)} \in \lrp(W) \wedge \\
        \perm \in \readAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \readCond{\lin,W} \wedge\\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \writeCond{\lin,W} \wedge\\
        % we are excluding rwx pointers.
        \perm \neq \rwx \wedge \\
        % \perm = \rwx &\Rightarrow& \array[t]{l}\npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge \\
        %                            \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W} \endarray\\
        \perm = \rx &\Rightarrow& \array[t]{l}\npair{[\baddr,\eaddr]} \in \execCond{W} \wedge\\
        \npair{[\baddr,\eaddr]} \in \xReadCond{W} \wedge \\
                                  \lin = \normal \\ \endarray
      \end{array}
    \end{array}
    \right\}
  \end{array}
\]

@@

\begin{definition}[Reasonable configuration]
  \label{def:reasonable-conf}
  We say that an execution configuration $\Phi$ is reasonable up to $n$ steps with $(\ta,\stkb,\gsigrets,\gsigcloss)$ 
  iff for $n' \leq n$:
  \begin{itemize}
  \item \emph{Guarantee stack base address before call} If
    \begin{itemize}
    \item $\Phi$ points to $\src{\scall{\offpc,\offsigma}{r_1}{r_2}}$ in $\ta$
      for some $\src{r_1}$ and $\src{r_2}$
    \end{itemize}
    Then all of the following hold:
    \begin{itemize}
    \item $\src{\Phi}(\src{r_\stk}) =
      \src{\stkptr{\_,\stkb,\_,\_}}$
    \item $r_1 \neq \rtmp{1}$
    \item $n' = 0$ or $\Phi(\pcreg) + \calllen$ behaves reasonably up to $n'-1$ steps
    \end{itemize}
  \item \emph{Use return seals only for calls, use closure seals appropriately} If
    \begin{itemize}
    \item $\src{\Phi}$ points to $\src{\tcseal{r_1}{r_2}}$ in $\ta$ and $\Phi(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$
    \end{itemize}
    Then one of the following holds:
    \begin{itemize}
    \item $\src{\Phi}$ is inside $\src{\scall{\offpc,\offsigma}{r_1'}{r_2'}}$ and $\sigma \in \gsigrets$
    \item $\sigma \in \gsigcloss$ and one of the following holds:
      \begin{itemize}
      \item $\exec{\Phi(r_2)}$ and $n' = 0$ or $\Phi(r_2)$ behaves reasonably up to $n' - 1$ steps.
      \item $\nonExec{\Phi(r_2)}$ and $n' = 0$ or $\Phi(r_2)$ is reasonable up to $n' - 1$ steps in memory $\Phi.\ms$ and free stack $\Phi.\ms_\stk$.
      \end{itemize}
    \end{itemize}
  \item \emph{Don't store private stuff...} If
    \begin{itemize}
    \item $\src{\Phi}$ points to $\src{\tstore{r_1}{r_2}}$ in $\ta$, then
    \end{itemize}
    Then $n' = 0$ or $\Phi.\reg(r_2)$ is reasonable in memory $\Phi.\mem$ up to $n' -1$ step
  \item \emph{Don't leak private stuff...} If
    \begin{itemize}
    \item $\Phi \step[\ta,\stkb] \Phi'$
    \end{itemize}
    Then one of the following holds:
    \begin{itemize}
    \item All of the following hold:
      \begin{itemize}
      \item $\Phi'.\reg(\pcreg) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr')$ and $\Phi.\reg(\pcreg) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr)$
      \item $\Phi$ does not point to $\src{\txjmp{r_1}{r_2}}$ for some $\src{r_1}$ and $\src{r_2}$
      \item $\Phi$ does not point to $\src{\scall{\offpc,\offsigma}{r_1}{r_2}}$ for some $\src{r_1}$ and $\src{r_2}$, $\offpc$, $\offsigma$
      \item $n' = 0$ or $\Phi'$ is reasonable up to $n'-1$ steps
      \end{itemize}
      % \dominique{the following seems unnecessary: why would we allow trusted code to use a jump instruction to jump out of a trusted component? it can use call and xjmp for calls/returns/tailcalls}
    % \item $\Phi'.\reg(r)$ is reasonable in memory $\Phi'.\mem$ and free stack $\Phi'.\ms_\stk$ up to $n'-1$ steps for all $r$ (including $\pcreg$)
    \item
      \begin{itemize}
      \item $\Phi$ points to $\src{\scall{\offpc,\offsigma}{r_1}{r_2}}$ for some $\src{r_1}$ and $\src{r_2}$
      \item $n' = 0$ or $\Phi.\reg(r)$ is reasonable in memory $\Phi.\mem$ and free stack $\Phi.\ms_\stk$ up to $n'-1$ steps for all $r \neq \pcreg$
      \end{itemize}
    \item
      \begin{itemize}
      \item $\Phi$ points to $\src{\txjmp{r_1}{r_2}}$ for some $\src{r_1}$ and $\src{r_2}$
      \item $n' = 0$ or $\Phi.\reg(r)$ is reasonable in memory $\Phi.\mem$ and free stack $\Phi.\ms_\stk$ up to $n'-1$ steps for all $r \neq \pcreg$
      \end{itemize}
    \end{itemize}
  \end{itemize}
\end{definition}
